RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-19 main.tex
:construction: Update layout

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}

@@

			By \gls{mrc} over $N$ primary blocks, the effective backscatter \gls{snr} is increased by $N$ times, and the total achievable for nodes with equiprobable inputs is \cite{Wang2014a}

@@

			\resizebox{0.75\columnwidth}{!}{

@@

		Fig. \ref{fi:region_comparison} presents the achieve rate points by different scattering applications when $Q=1$, $K=1$, $M=4$ and $N=1000$.
	\end{subsection}

	\begin{subsection}{Input Distribution versus Link Priority}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical instances of node input distribution for different weights.}
			\label{fi:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig. \ref{fi:distribution_weights}, where \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are two representative instances.
		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
		gradually progresses from slightly skewed to completely biased.
		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
		In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
	\end{subsection}

	\begin{subsection}{Achievable Rates versus Energy Discretization Bits}
		\begin{figure}[!t]
			\subfloat[Primary Rate\label{fi:rate_bits_primary}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/rate_bits_primary.tex}
				}
			}
			\subfloat[Total Backscatter Rate\label{fi:rate_bits_backscatter}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/rate_bits_backscatter.tex}
				}
			}
			\caption{Average achievable primary and total backscatter rates for different energy discretization bits for $\rho=0$.}
			\label{fi:rate_bits}
		\end{figure}
		We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average RIScatter performance.
		For a fixed input distribution and active beamforming, Fig. \ref{fi:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
		We observe the primary rate is a constant for different $b$ as expected from Remark \ref{re:backscatter_decision}.
		This conclusion holds for arbitrary $\rho$ because the randomness of reflection patterns over time can always be eliminated upon successful backscatter decoding.
		When the nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover their reflection patterns at each primary block.
		Otherwise, the reflection patterns of all nodes are fully deterministic, and the state index tuple can be fed back to the user together with \gls{csi}.
		We also notice increasing $b$ boosts the total backscatter rate and the benefit becomes marginal when $b$ is sufficiently large ($2^b \gg \mathrm{card}(\mathcal{L})$).
		This is because a larger $b$ allows the decision regions to be constructed from narrower energy bins, which mitigates the transformation loss from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete}.
		Therefore, we conclude a proper selection of $b$ is the key to balance backscatter performance and computational complexity.
	\end{subsection}

	\begin{subsection}{Rate Region by Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution\label{fi:region_distribution}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming\label{fi:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold\label{fi:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
				``BSP'' means backscatter symbol period.
			}
		\end{figure}
		The average achievable primary-total-backscatter rate regions of various input distribution, active beamforming, and decision threshold schemes are explored in this study.

@@

	\begin{subsection}{Rate Region versus Configuration}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fi:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fi:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fi:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fi:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\subfloat[Disk Radius\label{fi:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
				``PSP'' means primary symbol period.
			}
			\label{fi:region_config}
		\end{figure}
		In this study, we investigate the impact of system configuration on the average achievable rate regions.
		\begin{subsubsection}{Number of Nodes}
			Fig. \subref*{fi:region_tags} reveals how the number of two-state RIScatter nodes $K$ influence the primary-backscatter tradeoff.
			We observe the total backscatter rate roughly scales proportionally with the number of nodes, and the decrease of individual rate is unobvious.
			This demonstrates the proposed low-complexity semi-coherent energy detector performs reasonably well for a moderate $K$.
			On the other hand, we observe adding RIScatter nodes can also boost the achievable primary rate.
			The reason is the nodes can exploit the additional propagation path for a constructive primary signal superposition that enjoys a ``squared law'' similar to \gls{ris}.
		\end{subsubsection}

>>>>

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}

@@

			By \gls{mrc} over $N$ primary blocks, the total achievable for nodes with equiprobable inputs is \cite{Wang2014a}

@@

			\resizebox{0.65\columnwidth}{!}{

@@

		Fig. \ref{fi:region_comparison} presents the typical achieve rate points of different scattering applications for $Q=1$, $K=1$, $M=4$ and $N=1000$.
		First, we observe both \gls{bbc} and \gls{sr} can achieve the highest backscatter rate with coherent detection over the receive energy and intermediate signal, respectively.
		This is because repetition coding with \gls{mrc} over $N$ primary blocks effectively increases the backscatter \gls{snr} by $N$ times, and the information loss due to the signal-to-energy conversion on top may be insignificant.
		However, the asymptotic primary and backscatter rate analysis only provides upper bounds for \gls{sr}.
		Using a very large $N$ not only reduces the system throughput\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical symbol period ratio $N$ between \num{1} and \num{100}.} but also requires the operation-intensive \gls{sic} over each primary block.
		When the duration of primary and backscatter symbol are comparable, the randomly scattered signals should be modelled as interference to primary link rather than quasi-static multipath components, and the achievable rate point of \gls{sr} will move towards the origin.
		On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.

		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
		% ! SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and non-coherent detection can also achieve reasonable performance?
		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
		% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large

		Backscatter advantage of SR using SIC is prominent for a smaller N
		% correlation by double modulation improves the detection performance
		% when $N$ is sufficiently large.
	\end{subsection}

	\begin{subsection}{Input Distribution under Different Weights}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/distribution_weights.tex}
			}
			\caption{Typical reflection state distribution under different weights for $Q=1$, $K=1$, $M=4$ and $N=20$.}
			\label{fi:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate each RIScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights in Fig. \ref{fi:distribution_weights}.
		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
		gradually progresses from slightly skewed to completely biased.
		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the RIScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with equiprobable inputs, and some states may end up unused since they cannot produce enough energy difference over the existing alphabet.
		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the primary equivalent channel strength, and \num{0} at the others.
		In this case, the reflection pattern over time is fully deterministic, and the RIScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		Those observations meet our s that RIScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
		For the \gls{bcd} algorithm, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
	\end{subsection}

	% \begin{subsection}{Achievable Rates versus Energy Discretization Bits}
	% 	\begin{figure}[!t]
	% 		\subfloat[Primary Rate\label{fi:rate_bits_primary}]{
	% 			\resizebox{0.48\columnwidth}{!}{
	% 				\input{assets/simulation/rate_bits_primary.tex}
	% 			}
	% 		}
	% 		\subfloat[Total Backscatter Rate\label{fi:rate_bits_backscatter}]{
	% 			\resizebox{0.48\columnwidth}{!}{
	% 				\input{assets/simulation/rate_bits_backscatter.tex}
	% 			}
	% 		}
	% 		\caption{Average achievable primary and total backscatter rates for different energy discretization bits for $\rho=0$.}
	% 		\label{fi:rate_bits}
	% 	\end{figure}
	% 	We now reveal how the analog-to-digital conversion of feasible threshold domain from $\mathbb{R}_+^{L+1}$ to $\mathcal{T}^{L+1}$ affects the average RIScatter performance.
	% 	For a fixed input distribution and active beamforming, Fig. \ref{fi:rate_bits} shows the impact of energy discretization bits $b$ on the average achievable rates when $\rho=0$.
	% 	We observe the primary rate is a constant for different $b$ as expected from Remark \ref{re:backscatter_decision}.
	% 	This conclusion holds for arbitrary $\rho$ because the randomness of reflection patterns over time can always be eliminated upon successful backscatter decoding.
	% 	When the nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover their reflection patterns at each primary block.
	% 	Otherwise, the reflection patterns of all nodes are fully deterministic, and the state index tuple can be fed back to the user together with \gls{csi}.
	% 	We also notice increasing $b$ boosts the total backscatter rate and the benefit becomes marginal when $b$ is sufficiently large ($2^b \gg \mathrm{card}(\mathcal{L})$).
	% 	This is because a larger $b$ allows the decision regions to be constructed from narrower energy bins, which mitigates the transformation loss from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete}.
	% 	Therefore, we conclude a proper selection of $b$ is the key to balance backscatter performance and computational complexity.
	% \end{subsection}

	\begin{subsection}{Rate Region by Different Schemes}
		% \begin{figure}[!t]
		% 	\centering
		% 	\subfloat[Input Distribution\label{fi:region_distribution}]{
		% 		\resizebox{0.65\columnwidth}{!}{
		% 			\input{assets/simulation/region_distribution.tex}
		% 		}
		% 	}
		% 	\\
		% 	\subfloat[Active Beamforming\label{fi:region_beamforming}]{
		% 		\resizebox{0.65\columnwidth}{!}{
		% 			\input{assets/simulation/region_beamforming.tex}
		% 		}
		% 	}
		% 	\\
		% 	\subfloat[Decision Threshold\label{fi:region_threshold}]{
		% 		\resizebox{0.65\columnwidth}{!}{
		% 			\input{assets/simulation/region_threshold.tex}
		% 		}
		% 	}
		% 	\caption{
		% 		Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
		% 		``BSP'' means backscatter symbol period.
		% 	}
		% \end{figure}
		\begin{figure*}[!t]
			\centering
			\subfloat[Input Distribution\label{fi:region_distribution}]{
				\resizebox{0.32\textwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\subfloat[Active Beamforming\label{fi:region_beamforming}]{
				\resizebox{0.32\textwidth}{!}{
					\input{assets/simulation/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold\label{fi:region_threshold}]{
				\resizebox{0.32\textwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
				``BSP'' means backscatter symbol period.
			}
		\end{figure*}
		The average achievable primary-total-backscatter rate regions of various input distribution, active beamforming, and decision threshold schemes are explored in this study.

@@

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fi:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fi:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fi:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\subfloat[Symbol Period Ratio\label{fi:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fi:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\subfloat[Disk Radius\label{fi:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
				``PSP'' means primary symbol period.
			}
			\label{fi:region_config}
		\end{figure}
		In this study, we investigate the impact of system configuration on the average achievable rate regions.
		\begin{subsubsection}{Number of Nodes}
			Fig. \subref*{fi:region_tags} reveals how the number of two-state RIScatter nodes $K$ influence the primary-backscatter tradeoff.
			We observe the total backscatter rate roughly scales proportionally with the number of nodes, and the decrease of individual rate is unobvious.
			This demonstrates the proposed low-complexity semi-coherent energy detector performs reasonably well for a moderate $K$.
			On the other hand, we observe adding RIScatter nodes can also boost the achievable primary rate.
			The reason is the nodes can exploit the additional propagation path for a constructive primary signal superposition that enjoys a ``squared law'' similar to \gls{ris}.
		\end{subsubsection}
